Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-22 paper.qmd
Intro section for link plot

>>>>

It’s important to access the \gD{} layout and the generated model overlaid on data in \pD{} together to understand whether it fits the points everywhere, fits better in some places, or simply mismatches the pattern. The \gD{} layout and the langevitour view with the model are linked together via rectangular brushes; when a brush is active, points will be highlighted in the adjacent view. Because the langevitour is dynamic, brush events that become active will pause the animation, so that a user can interrogate the current view. The interface is constructed as a **browsable HTML widget** specifically designed for interactive data analysis.
